The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-09-25 paper/ms.tex
gammaR distribn: update plot

The above approach ignores incompleteness for binary systems.
If we set the limiting flux to give 100\% completeness for single stars, we 
will unwittingly select binaries near that flux limit, for which dilution 
will push transit signals below the detection threshold.
This is because a flux limit maps onto three distinct maximum 
detection distances for a population of single stars and twin binaries:
\begin{enumerate}
\item $d_{{\rm max},s}$: the maximum distance out to which the desired type 
	of planet is detectable around single stars.
	These are the selected ``searchable, single stars''.
%
\item $d_{{\rm max},d}$: the maximum distance out to which double stars
  are selected (down to the same minimum flux as that defining $d_{{\rm 
  max},s}$). 
  This is different from $d_{{\rm max},d}^{\rm p}$, the maximum
  distance out to which planets are detectable around double stars. For a 
  population with fixed  $\gamma_R$, since ${\rm S/N} \propto \mathcal{D} 
  L^{-1/2} d$,
  \begin{equation}
    d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
    (1 + \gamma_R)^{-1} d_{{\rm max},d}.
  \end{equation}
  For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
  are in fact binary systems can yield detectable planets.

@@

Counting the number of desired stars, $N_s$ is the same as in 
Sec.~\ref{sec:model_1}. However
\begin{equation}
N_d(\gamma_R) = n_d \frac{4\pi}{3} d_{\rm max,d}^3(L_1, \gamma_R, F_{\rm 
	min})
\end{equation}
for
\begin{equation}
d_{\rm max,d}(L_1, \gamma_R, F_{\rm min}) =
d_{\rm max,s}(L_1, F_{\rm min})\times (1+\gamma_R)^{1/2},
\end{equation}
where $d_{\rm max,s}$ is given by Eq.~\ref{eq:d_max}.

@@

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/q_distribn_mag_limited.pdf}
	\end{center}
	\caption{The distribution of the mass ratio for a magnitude limited 
		sample of binary stars. The empirical mass-luminosity relation is shown
		in Fig.~\ref{fig:mass_luminosity}.
		The underlying mass ratios are drawn from Eq.~\ref{eq:mass_ratio} -- a 
		\textit{uniform} distribution in a volume-limited sample!
		The entire bias can be understood analytically 
		(Eq.~\ref{eq:pdf_q_mag_limited}) to reasonable precision. 
	}
	\label{fig:q_distribn_mag_limited}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/gammaR_distribn_mag_limited.pdf}
	\end{center}
	\caption{The distribution of the luminosity ratio for a magnitude limited 
		sample of binary stars. ${\rm BF} = 0.45$ [Duchene and Kraus 2013]; 
		total 
		number density from Bovy 2017; $M(L)$ relation from 
		Fig.~\ref{fig:mass_luminosity}; mass ratios are drawn from 
		Eq.~\ref{eq:mass_ratio}.}
	\label{fig:gammaR_distribn_mag_limited}
\end{figure}

Before blindly plugging in Eq.~\ref{eq:mass_ratio}'s assumed mass ratio 
distribution to find the expected number of double systems, we must
emphasize that Eq.~\ref{eq:mass_ratio}'s distribution applies only for 
volume-limited samples.
If one is interested in a SNR-limited transit survey (or really any
magnitude-limited survey), the Malmquist-like bias associated with binarity, 
and affecting the distribution of binary mass ratios, must be included.

>>>>

The above approach ignores incompleteness for binary systems.
If we set the limiting flux to give 100\% completeness for single stars, we 
will unwittingly select binaries near that flux limit, for which dilution 
will push transit signals below the detection threshold.
This is because a flux limit maps onto three distinct maximum 
detection distances for a population of single stars and twin binaries:
\begin{enumerate}
\item $d_{{\rm max},s}$: the maximum distance out to which the desired type 
	of planet is detectable around single stars.
	These are the selected ``searchable, single stars''.
%
\item $d_{{\rm max},d}$: the maximum distance out to which double stars
  are selected (down to the same minimum flux as that defining $d_{{\rm 
  max},s}$). 
  This is different from $d_{{\rm max},d}^{\rm p}$, the maximum
  distance out to which planets are detectable around double stars. For a 
  population with fixed  $\gamma_R$, since ${\rm S/N} \propto \mathcal{D} 
  L^{1/2} d^{-1}$,
  \begin{equation}
    d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
    (1 + \gamma_R)^{-1} d_{{\rm max},d}.
  \end{equation}
  For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
  are in fact binary systems can yield detectable planets.

@@

Counting the number of desired stars, $N_s$ is the same as in 
Sec.~\ref{sec:model_1}. However
\begin{equation}
N_d(\gamma_R) = n_d \frac{4\pi}{3} d_{\rm max,d}^3(\gamma_R)
\end{equation}
for
\begin{equation}
d_{\rm max,d}(\gamma_R) =
d_{\rm max,s}\times (1+\gamma_R)^{1/2},
\end{equation}
where $d_{\rm max,s}$ is given by Eq.~\ref{eq:d_max}.

@@

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/q_distribn_mag_limited.pdf}
	\end{center}
	\caption{The distribution of the mass ratio for a magnitude limited 
		sample of binary stars. The underlying mass ratios are drawn from 
		Eq.~\ref{eq:mass_ratio} -- a \textit{uniform} distribution in a 
		volume-limited sample.
		The entire bias can be understood analytically 
		(Eq.~\ref{eq:pdf_q_mag_limited}) to good precision. 
        The numerical comparison uses the empirical mass-luminosity relation 
        shown in Fig.~\ref{fig:mass_luminosity}.
	}
	\label{fig:q_distribn_mag_limited}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/gammaR_distribn_mag_limited.pdf}
	\end{center}
	\caption{The distribution of the luminosity ratio for a magnitude limited 
		sample of binary stars. Despite the preference in the sample towards 
		large $q$ binaries (Fig.~\protect\ref{fig:q_distribn_mag_limited}), 
		the bias is towards small $\gamma_R$ binaries because of the steepness 
		of the mass-luminosity relation.
        The underlying mass ratios are uniform in volume.
        The numerical comparison uses the empirical mass-luminosity relation 
        shown in Fig.~\ref{fig:mass_luminosity}.       
    }
	\label{fig:gammaR_distribn_mag_limited}
\end{figure}

Before blindly plugging in Eq.~\ref{eq:mass_ratio}'s assumed mass ratio 
distribution to find the expected number of double systems, we must
emphasize that Eq.~\ref{eq:mass_ratio}'s distribution applies only for 
volume-limited samples.
If one is interested in a SNR-limited transit survey (or really any
magnitude-limited survey), the Malmquist-like bias associated with binarity
must be included.
